Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/related.tex
added to related work

\paragraph{}

>>>>

\paragraph*{Configuration Automation}
Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way. 
However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.
